Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-09-08 graviton spectra/content/e16.tex
merg

\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}

@@

\surya{we should pin down what values of $\Delta, R_i$ appear for us}

@@

\begin{conj}\label{conj:e16gravitonrep}
For $j\geq -1$, the minimal twist of the $(j+2)$-weight graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
\end{conj}

\begin{rmk}\label{rmk:e16enhance}
This conjecture implies that the minimal twist of these graviton representations, which is a priori a module for the minimally twisted 3d $\mc N=8$ superconformal algebra $\mf{osp}(6|2)$, is in fact a module for the larger infinite dimensional super-Lie algebra $E(1|6)$. This can be thought of as analogous to the enhancement of conformal symmetries to the action of the Witt algebra of vector fields in 2d chiral conformal field theory. Such symmetry enhancements in 3 dimensions is the topic of joint work in progress with Garner and Williams.
\end{rmk}

>>>>

%\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}

@@

@@

\begin{conj}\label{conj:e16gravitonrep}
For $j\geq -1$, the minimal twist of the $(j+2)$-weight graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} (denoted $B[0]_{j/2+1}^{(0,0,0,j+2)}$ in \cite{cordova2016multiplets}) is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
\end{conj}

\begin{rmk}\label{rmk:e16enhance}
This conjecture implies that the minimal twist of these graviton representations, which is a priori a module for the minimally twisted 3d $\mc N=8$ superconformal algebra $\mf{osp}(6|2)$, is in fact a module for the larger infinite dimensional super-Lie algebra $E(1|6)$. This can be thought of as analogous to the enhancement of conformal symmetries to the action of the Witt algebra of vector fields in 2d chiral conformal field theory. Such symmetry enhancements in 3 dimensions is discussed in \cite{GRW}.
\end{rmk}
